### 2009-09-16 trunk/latex/paper1/contents.tex
referencias das redes

\begin{table}
\caption{Results for the classification of synthetic networks}
Table: Model | Networks classified as software-like
\begin{tabular}{ l | r }
\hline
Model & Networks classified as software-like \\
\hline \\
\hline
BCR+ & 21.18\% \\ % 2012 / 9500
CGW  & 19.40\% \\  % 7524 / 38790
LF   & 31.25\% \\ %  405 / 1296
\hline
\end{tabular}
\label{tab:results}
\end{table}

@@

\begin{table}
\caption{Rules for predicting the classification of a synthetic network. S
stands for software-like and N stands for non software like.}
Table: Model | Networks classified as software-like
\begin{tabular}{ l | r }
\hline
Model & Rule & Accuracy \\
\hline \\
\hline
\multirow{2}{*}{BCR+}
     & $\alpha \ge 0.7 \Rightarrow S$ & \multirow{2}{*}{82.4\%}  \\ 
     & $\alpha < 0.7 \Rightarrow N$ & \\

CGW  & $p_1 \ge 0.5 \Rightarrow S$ & 82.3\% \\  
     & $p_1 < 0.5 \Rightarrow N$ & \\

LF   & $\gamma \ge 2.44$ & 78.9\% \\ 
     & $\gamma \ge 2.44$ &  \\ 
\hline
\end{tabular}
\label{tab:rules}
\end{table}

== LF ==
degexp
        < 2.4400000000000004    ->
        >= 2.4400000000000004   -> *
        (1023/1296 instances correct) (78.9352%)

(removendo parametro degexp:)
maxk:
        < 319.5 -> *
        >= 319.5        ->
        (957/1296 instances correct) (73.8426%)

== BCR ==
alpha:
        < 0.7   -> *
        >= 0.7  ->
        (7832/9500 instances correct) (82.4421%)

(removendo parametro alpha:)
gamma:
        < 0.1   ->
        >= 0.1  -> *
        (7564/9500 instances correct) (79.6211%)

== CGW (C++) ==
p1:
        < 0.5   -> *
        >= 0.5  ->
        (31920/38790 instances correct) (82.2892%)

(removendo parametro p1:)
dá uma resposta sem sentido

Despite its simplicity, 1R found rules with high precision. These rules allow
one to know if a particular combination of parameter values is likely to lead to
software-like networks.

@@

In a future work, we intend to use synthetic networks in the evaluation of
software clustering algorithms that were previously studied with real networks
\cite{Wu2005}. After that we will be able to compare the results obtained by
both approaches.

@@

Other networks:

3 circuit networks (circuit-s208 circuit-s420 circuit-s838)

5 facebook networks (facebook-Caltech36 facebook-Georgetown facebook-Oklahoma
facebook-Princeton facebook-UNC28)

5 language networks (lang-english  lang-french lang-japanese lang-spanish)

43 metabolic networks

3 protein networks (protein-a4j protein-AOR protein-eaw)

2 social networks (social-leader social-prison)

other networks:

polblogs

yeast

beta3sreduced
celegansneural

>>>>

\begin{table}
\caption{Results for the classification of synthetic networks}
Table: Model | Networks classified as software-like
\begin{tabular}{ l | l }
\hline
Model & Networks classified as software-like \\
\hline \\
\hline
BCR+ & 21.18\% \\ % 2012 / 9500
CGW  & 19.40\% \\  % 7524 / 38790
LF   & 31.25\% \\ %  405 / 1296
\hline
\end{tabular}
\label{tab:results}
\end{table}

@@

\begin{table}
\caption{Rules for predicting the classification of a synthetic network. S
stands for software-like and N stands for non software like.}
Table: Model | Networks classified as software-like
\begin{tabular}{ l | l | l }
\hline
Model & Rule & Accuracy \\
\hline \\
\hline
\multirow{2}{*}{BCR+}
     & $\alpha \ge 0.7 \Rightarrow S$ & \multirow{2}{*}{82.4\%}  \\ 
     & $\alpha < 0.7 \Rightarrow N$ & \\ 
\hline
\multirow{2}{*}{CGW}
     & $p_1 \ge 0.5 \Rightarrow S$ & \multirow{2}{*}{82.3\%} \\  
     & $p_1 < 0.5 \Rightarrow N$ & \\  
\hline
\multirow{2}{*}{LF}   
     & $\gamma \ge 2.44$ & \multirow{2}{*}{78.9\%} \\ 
     & $\gamma \ge 2.44$ &  \\ 
\hline
\end{tabular}
\label{tab:rules}
\end{table}

The rules are very simple and, thus, easy to follow. Despite their simplicity,
they have high accuracy, approximately 80\% in all models.  
%These rules allow one to know if a particular combination of parameter values
%is likely to lead to software-like networks.

@@

In a future work, we intend to use synthetic networks in the evaluation of
software clustering algorithms that were previously studied with real networks
\cite{Wu2005}. After that we will be able to compare the results obtained by
the approaches.

@@

Networks from other domains:

3 electronic circuit networks (circuit-s208 circuit-s420 circuit-s838)
\cite{Milo2004}

5 friendship networks (facebook-Caltech36 facebook-Georgetown facebook-Oklahoma
facebook-Princeton facebook-UNC28) \cite{Traud2008}

4 word adjacency networks (lang-english lang-french lang-japanese lang-spanish)
\cite{Milo2004}

3 protein structure networks (protein-a4j protein-AOR protein-eaw)
\cite{Milo2004}

2 social networks of positive sentiment (social-leader social-prison)
\cite{Milo2004}

43 metabolic networks \cite{Jeong2000}.

Protein interaction network for yeast \cite{Jeong2001}

polblogs \cite{Adamic2005}

beta3sreduced
celegansneural \cite{Watts1998}
